---
title: "STB Assessment"
author: "Fang Yu"
date: "2024-07-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
options(scipen = 999)
library(tidyverse)
library(readxl)
library(klaR)
```

### Question 1
```{r}
#Setup for Question 1
setwd("D:/Projects/stb_assessment") #Set to repository directory
data = read_excel("data/mock_survey_data_3.xlsx")
```
#### a)	Describe the approach you will take and data fields you would look into when it comes to data preparation 

##### Preliminary Inspection
```{r}
glimpse(data)
```

```{r}
# Fixing column names for occupation
data <- rename(data, Occupation = `Occupation...17`, Sector = `Occupation...18`)
```

##### Data Cleaning

```{r}
# Convert to appropriate data types
shopping_columns <- grep("^shopping_", names(data), value = TRUE)
#travel_columns <- grep("^Travel", names(data), value = TRUE)

# Convert identified columns to double
data[shopping_columns] <- lapply(data[shopping_columns], as.double)
#data[travel_columns] <- lapply(data[travel_columns], as.double)
```

```{r}
# Checking for Missing Values
missing_values <- colSums(is.na(data))
print("Missing Values:")
print(missing_values)

# Checking for Duplicates
duplicates <- sum(duplicated(data))
print("Duplicates:")
print(duplicates)
```
```{r}
# Checking if case is a unique identifier
data %>% count(case) %>% arrange(desc(n))
```
```{r}
# Give NA cases unique identifiers
max_case <- max(data$case, na.rm = TRUE)

# Generate unique values for NA entries
data <- data %>%
  mutate(case = ifelse(is.na(case), max_case + row_number(), case))
```

```{r}
# Fixing shopping_xxx values
data = data %>%
  mutate(shopping_fash = ifelse(is.na(shopping_fash), 0, shopping_fash),
         shopping_food = ifelse(is.na(shopping_food), 0, shopping_food),
         shopping_gifts = ifelse(is.na(shopping_gifts), 0, shopping_gifts),
         shopping_others = ifelse(is.na(shopping_others), 0, shopping_others),
         shopping_any = shopping_fash + shopping_jewllery + shopping_watches 
         + shopping_wellness + shopping_gifts + shopping_consumertech
         + shopping_antiques + shopping_others)
```

```{r}
# Check for missing values across all three terminal
missing_rows <- data %>%
  filter(is.na(Air_Terminal) & is.na(Sea_Terminal) & is.na(Land_Terminal))

# Display the rows with all three features missing
print(missing_rows)
```
```{r}
# Find most frequent terminal for tourists from Vietnam, Thailand and Italy
data %>% filter(`Country of Residence` == "Vietnam") %>% count(Land_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Vietnam") %>% count(Sea_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Vietnam") %>% count(Air_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Thailand") %>% count(Land_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Thailand") %>% count(Sea_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Thailand") %>% count(Air_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Italy") %>% count(Land_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Italy") %>% count(Sea_Terminal) %>% arrange(desc(n))

data %>% filter(`Country of Residence` == "Italy") %>% count(Air_Terminal) %>% arrange(desc(n))
```
```{r}
# Filling in Missing Values for Terminal
data <- data %>%
  mutate(
    Air_Terminal = ifelse(case == 699, 2, Air_Terminal),
    Air_Terminal = ifelse(case == 811, 3, Air_Terminal),
    Air_Terminal = ifelse(case == 824, 1, Air_Terminal)
  )
```

```{r}
# Filling in Missing Values for Main Hotel
max_hotel <- max(data$MainHotel, na.rm = TRUE)

# Generate unique values for NA entries
data <- data %>%
  mutate(MainHotel = ifelse(is.na(MainHotel), as.character(as.double(max_hotel) + 1), MainHotel),
         MainHotel = ifelse(MainHotel %in% c(991,992,993,994,999,9996,9999),as.character(as.double(max_hotel) + 1), MainHotel))
```

##### Exploratory Data Analysis

```{r}
# Viewing Summary Statistics
summary(data)
```

#### b) Highlight the data idiosyncrasies / issues you found in this dataset and how would you deal with it.

##### Negative Values for Expenditure

```{r}
# Setting `tototh` column values to zero is negative
data <- data %>%
  mutate(tototh = ifelse(tototh < 0, 0, tototh))

# Correcting total expenditure column
data <- data %>%
  mutate(tot.exp = totacc + totfnb + tottran + totbiz + totedu + totmedi + tototh + totshopping_rep)
```

##### Main Purpose of Visit does not match Purpose of Visit

```{r}
# Main Purpose of Visit does not Match Purpose of Visit
data %>% filter(`Purpose of Visit` == "Healthcare + Accompanying Pax") %>% dplyr::select("Main Purpose of Visit" ) %>% distinct()
```
```{r}
# Obtain all distinct purpose of visits into a vector
specific_purposes = data %>% dplyr::select(`Main Purpose of Visit`) %>% distinct() %>% pull(`Main Purpose of Visit`)
general_purposes = data %>% dplyr::select(`Purpose of Visit`) %>% distinct() %>% pull(`Purpose of Visit`)

print(general_purposes)
print(specific_purposes)
```
```{r}
# Fix the correct Purpose of Visit based on the Main Purpose of Visit
# New Purposes
purpose_map <- list(
  Leisure = c(
    "Holiday/ Rest & Relax", "Visiting friends/ relatives (who are not international", "To take or join a regional or international cruise",
    "Stopover (a planned stop of at least one night)", "Cultural Festivals (e.g. Lunar New Year, Deepavali, Hari",
    "Sightseeing/ Attractions", "Company sponsored holiday/incentive programme (a. Venue of", "To shop/ attend shopping events in Singapore Event name",
    "Music-related (e.g. concerts, festivals, etc) Event name", "Partying at clubs/ pubs/ dance parties (e.g. Avalon &",
    "To visit the integrated resorts(e.g. Marina Bay Sands,", "To experience the food/ food events in Singapore Event name",
    "Others (e.g. leisure exhibitions, cinema, recreational", "Personal Enrichment (cooking, batik painting class, etc)",
    "Sporting (e.g. rugby matches, marathons, golf tournaments,", "Performing Arts (e.g. musicals, theatre, dance, opera, etc)",
    "To experience different cultures", "To experience the nightlife in Singapore (e.g. all late", "Family Entertainment (e.g. kid’s music & theatre, ice/ magic"
  ),
  `Business + Accompanying Pax` = c(
    "General business purpose", "Accompanying a business visitor", "Corporate/ business meetings   (a. Venue of corporate/",
    "Convention/ conference", "Others - Work Related (e.g. visa, insurance, etc)", "Exhibition/ trade show",
    "Job Opportunities"
  ),
  `Education + Accompanying Pax` = c(
    "Visiting an international student (relative or friend)", "Accompanying an international student (relative or friend)",
    "School trips", "Study mission (including government study trips)", "Gather information/ facts on the education services in",
    "Skills development/ skills training/ vocational training", "In-house company training (Name of company)",
    "Student enrichment programmes (e.g. language courses, camps,", "Executive training, including training workshops and",
    "Student events (e.g. sports & other competitions, music"
  ),
  `Healthcare + Accompanying Pax` = c(
    "Outpatient consultation/ treatment (e.g. with General", "In-patient (hospitalization) treatment", "Accompanying a healthcare/ medical visitor for Outpatient",
    "Accompanying  a healthcare/ medical visitor for In-patient", "Day-surgery (with no hospitalization)", "Accompanying a healthcare/ medical visitor for Day-surgery",
    "Gather information/ facts on the healthcare services in"
  ),
  `Others/Refused` = c(
    "Others - Personal (e.g. weddings, funerals, etc)", "Pls specify", "Others, please specify", "Using Singapore as a hub to go to other destinations:", "Using Singapore as a hub to go to other destinations: Stop"
  )
)

# Create a reverse lookup list
reverse_map <- unlist(purpose_map)
names(reverse_map) <- rep(names(purpose_map), sapply(purpose_map, length))

# Create the new column with the general purpose
data <- data %>%
  mutate(`Purpose of Visit` = names(reverse_map[match(`Main Purpose of Visit`, reverse_map)]))
```

##### Illogical Data Entries for Travel Companions
```{r}
# Check for Incosistencies for Travel Companionship
data %>% 
  dplyr::select(starts_with("Travel companion")) %>% 
  mutate_all(as.double) %>% 
  rowSums() %>% table()

data %>%
  filter(`Travel companion - Alone`  == "1") %>% dplyr::select(starts_with("Travel companion")) %>% 
  mutate_all(as.double) %>% 
  rowSums() %>% table()
```


##### Explaratory Data Analysis
```{r}
# Viewing demographics of respondents
k <- 10

# Calculate the frequency of each category and select the top k
top_k_data <- data %>%
  count(`Country of Residence`) %>%
  top_n(k, n) %>%
  arrange(desc(n))

# Generate the frequency count chart for the top k categories
ggplot(top_k_data, aes(x = reorder(`Country of Residence`, -n), y = n)) +
  geom_bar(stat = "identity") +
  labs(title = paste("Top", k, "Most Frequent Country of Residence"),
       x = "Country of Residence",
       y = "Frequency") +
  theme_minimal()
```

```{r}
data_entry <- data %>%
  summarize(
    Air_Entry = sum(!is.na(Air_Terminal)), 
    Land_Entry = sum(!is.na(Land_Terminal)), 
    Sea_Entry = sum(!is.na(Sea_Terminal))
  )

# Reshape the data to a long format for easier plotting
data_entry_long <- data_entry %>%
  pivot_longer(everything(), names_to = "Entry_Type", values_to = "Count")

ggplot(data_entry_long, aes(x = Entry_Type, y = Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Count of Entry Type",
       x = "Entry Type",
       y = "Frequency") +
  theme_minimal()

```

### Question 2
#### Part 1: Clustering with Kmodes
##### Feature Engineering
```{r}
# Mode of Entry
data = data %>% mutate(
  AirEntry = ifelse(!is.na(Air_Terminal),1,0),
  LandEntry = ifelse(!is.na(Land_Terminal),1,0),
  SeaEntry = ifelse(!is.na(Sea_Terminal),1,0),
  )

categorical_variables = c('Country of Residence', 'Purpose of Visit', 'AirEntry', 'LandEntry', 'SeaEntry', 'Gender', 'Marital Status','Travel companion - Alone' )

data_for_clustering = data[categorical_variables]

```

```{r}
# Run Kmodes

costs <- numeric(10)

for (k in 1:10) {
  set.seed(42)
  kmodes_result <- kmodes(data_for_clustering, modes = k, iter.max = 20, weighted = FALSE)
  costs[k] <- kmodes_result$withindiff
}

# Plot the Elbow Method
qplot(1:10, costs, geom = "line") +
  labs(title = "Elbow Method for Optimal Number of Clusters", x = "Number of Clusters", y = "Total Within-cluster Simple-matching Distance") +
  theme_minimal()
```

```{r}
# Run K-Modes clustering
set.seed(42)
kmodes_result <- kmodes(data_for_clustering, modes = 5, iter.max = 10, weighted = FALSE)

# Add cluster labels to the original dataset
data_for_clustering$Cluster <- kmodes_result$cluster

# Summarize the cluster profiles
cluster_profiles <- data_for_clustering %>%
  group_by(Cluster) %>%
  summarize(across(everything(), ~ names(sort(table(.), decreasing = TRUE))[1]))

print(cluster_profiles)

# Count the number of observations in each cluster
cluster_counts <- data_for_clustering %>%
  group_by(Cluster) %>%
  summarize(Count = n())

# Combine dataframes to obtain statistics
clusters <- inner_join(cluster_profiles, cluster_counts, by = "Cluster")

print(clusters)
```

### Part 2
#### Visitor Insights

```{r}
### Purpose of Visit
data %>% count(`Purpose of Visit`) %>%
  ggplot(aes(x = "", y = n, fill = `Purpose of Visit`)) +
    geom_bar(stat = "identity", width = 1) +
    coord_polar("y") +
    labs(title = "Pie Chart of Purpose of Visit", x = "", y = "") +
    theme_void() +
    theme(legend.title = element_blank(), plot.title = element_text(size = 14, face = "bold"))

### Main Purpose for Leisure
k <- 5

# Calculate the frequency of each category and select the top k
top_k_data <- data %>%
  filter(`Purpose of Visit` == "Leisure") %>%
  count(`Main Purpose of Visit`) %>%
  top_n(k, n) %>%
  arrange(desc(n))

# Generate the frequency count chart for the top k categories
ggplot(top_k_data, aes(x = reorder(`Main Purpose of Visit`, -n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = paste("Top", k, "Main Purpose of Visit for Leisure"),
       x = "Main Purpose of Visit",
       y = "Frequency") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 14, face = "bold"))

### Main Purpose for Business
# Calculate the frequency of each category and select the top k
top_k_data_biz <- data %>%
  filter(`Purpose of Visit` == "Business + Accompanying Pax") %>%
  count(`Main Purpose of Visit`) %>%
  top_n(k, n) %>%
  arrange(desc(n))

# Generate the frequency count chart for the top k categories
ggplot(top_k_data_biz, aes(x = reorder(`Main Purpose of Visit`, -n), y = n)) +
  geom_bar(stat = "identity") +
  labs(title = paste("Top", k, "Main Purpose of Visit for Business"),
       x = "Main Purpose of Visit",
       y = "Frequency") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(size = 14, face = "bold"))


### Duration of Stay by Purpose
data %>% group_by(`Purpose of Visit`) %>% summarize(Duration = median(`Length of Stay`)) %>%
  ggplot(aes(x=`Purpose of Visit`, y = `Duration`)) + geom_col() + labs(title = "Median Duration of Stay by Purpose") +
      theme_minimal() + theme(legend.title = element_blank(), plot.title = element_text(size = 14, face = "bold")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

### Gender and Marital Status
ggplot(data, aes(x = `Gender`, fill = `Marital Status`)) +
  geom_bar() +
  labs(title = "Frequency Counts of Gender by Marital status", x = "Gender", y = "Count") + theme_minimal() + theme(plot.title = element_text(size = 14, face = "bold"))

### Gender and First Time Visitors
ggplot(data, aes(x = `Gender`, fill = `First Visit To Singapore`)) +
  geom_bar() +
  labs(title = "Frequency Counts of Gender by First Visit to Singapore", x = "Gender", y = "Count") + theme_minimal() + theme(plot.title = element_text(size = 14, face = "bold"))

### Gender and Visiting Alone
ggplot(data, aes(x = `Gender`, fill = `Travel companion - Alone`)) +
  geom_bar() +
  labs(title = "Frequency Counts of Gender by Visiting Alone", x = "Gender", y = "Count") + theme_minimal() + theme(plot.title = element_text(size = 14, face = "bold"))

### Males Visiting Alone by Purpose
data %>%
  filter(`Gender` == "Male", `Travel companion - Alone` == 1) %>%
  count(`Purpose of Visit`) %>%
  ggplot(aes(x = reorder(`Purpose of Visit`, -n), y = n)) + 
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Frequency Counts of Purpose of Visits by Males Travelling Alone", x = "Purpose", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(size = 14, face = "bold")) 


### Gender and Travel Type
ggplot(data, aes(x = `Gender`, fill = `Travel Type`)) +
  geom_bar() +
  labs(title = "Frequency Counts of Gender by Travel Type", x = "Gender", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"))

### Marital Status and Travel Type
ggplot(data, aes(x = `Marital Status`, fill = `Travel Type`)) +
  geom_bar() +
  labs(title = "Frequency Counts of Marital Status by Travel Type", x = "Marital Status", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"))
```

#### Travel Companion and Hotel
```{r}
### Filtering out inconsistent entries and reducing dataset size to correct entries
corrections = data %>%
  filter(`MainHotel` != max(as.double(`MainHotel`))) %>%
  dplyr::select(starts_with("Travel companion")) %>% 
  mutate_all(as.double) %>% 
  rowSums()

data_reduced = data %>% filter(`MainHotel` != max(as.double(`MainHotel`))) %>%
  dplyr::select(`MainHotel`, starts_with("Travel companion")) %>%
  mutate(corrections = corrections) %>%
  filter(corrections != 0) %>% dplyr::select(-corrections)

data_reduced
```

```{r}
# Perform Chi-Square Test to determine correlation
data$MainHotel <- as.factor(data$MainHotel)

travel_companion_cols <- grep("^Travel companion", names(data), value = TRUE)

results <- list()  

for (col in travel_companion_cols) {
  contingency_table <- table(data[[col]], data$MainHotel)
  chi_square_result <- chisq.test(contingency_table)
  results[[col]] <- list(
    p_value = chi_square_result$p.value,
    chi_square_statistic = chi_square_result$statistic,
    conclusion = ifelse(chi_square_result$p.value < 0.01, 
                        "Significant correlation", 
                        "No significant correlation")
  )
}

for (col in names(results)) {
  cat("Results for:", col, "\n")
  print(results[[col]])
  cat("\n")
}

```

#### Viewing Hotel Insights

```{r}
# load hotel dataset
hotel_data = read_csv("data/hotel_info.csv") %>% mutate(MainHotel = as.factor(MainHotel))
data_reduced = data_reduced %>% inner_join(hotel_data, by = "MainHotel")
```
```{r}
# Create barplots to get top 5 hotels for each travel companion
for (col in travel_companion_cols) {
  
  filtered_data <- data_reduced %>% dplyr::select(col, `Hotel_Name`) %>% filter(!!sym(col) == 1)
  
  print(filtered_data)
  top_hotels <- filtered_data %>%
    count(`Hotel_Name`) %>%
    arrange(desc(n)) %>%
    top_n(5, n)
  
  
  dummy = ggplot(top_hotels, aes(x = reorder(`Hotel_Name`, -n), y = n)) +
    geom_bar(stat = "identity", fill = "steelblue") +
    theme_minimal() +
    labs(title = paste("Top 5 Hotels for", col),
         x = "Hotel",
         y = "Frequency") +
    theme_minimal() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), plot.title = element_text(size = 14, face = "bold"))
  
  print(dummy)

}

```
### K-Modes Analysis
```{r}
# All statistics
row0 = data %>% summarise(across(where(is.numeric), mean))
# Male Married Businessmen travelling alone
row1 = data %>% filter(`Purpose of Visit` == "Business + Accompanying Pax", `Gender` == "Male", `Marital Status` == "Married", `Travel companion - Alone` == "1") %>% summarise(across(where(is.numeric), mean))
# Married Couples travelling together for Leisure
row2 = data %>% filter(`Purpose of Visit` == "Leisure", `Marital Status` == "Married", `Travel companion - Alone` == "0") %>% summarise(across(where(is.numeric), mean))
# Single Females travelling with others for Leisure
row3 = data %>% filter(`Purpose of Visit` == "Leisure", `Gender` == "Female", `Marital Status` == "Single", `Travel companion - Alone` == "0") %>% summarise(across(where(is.numeric), mean))

# Combine Statistics
cluster_statistics = bind_rows(row0,row1,row2,row3) %>% dplyr::select(-c(case,year,month,Weights_QTR)) %>% mutate(Group = c("All", "Cat1", "Cat2", "Cat3")) %>% dplyr::select(Group, everything())

cluster_statistics
```

```{r}
# Shopping Preference Analysis
cluster_statistics_shopping = cluster_statistics %>% dplyr::select(Group, starts_with("shopping"))

cluster_statistics_shopping %>% ggplot(aes(x = Group, y = shopping_consumertech)) + geom_col(fill = "steelblue") +
  labs(title = "Shopping trends across clusters: Consumer Tech", x = "Cluster", y = "Mean") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"))
```
```{r}
# Expenditure Analysis
cluster_statistics_expenditure = cluster_statistics %>% dplyr::select(Group, starts_with("tot"))

cluster_statistics_expenditure %>% ggplot(aes(x = Group, y = tot.exp)) + geom_col(fill = "steelblue") +
  labs(title = "Expenditure: Total", x = "Cluster", y = "Mean") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"))

```